Ускорение семплирования из диффузионных моделей с использованием состязательных сетей

### 2023-05-02 slides/slides.tex
update slides

	\setbeamertemplate{footline}[page number]
	\setbeamersize{text margin left=1.5em, text margin right=2.0em}
}
\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}

@@

\begin{frame}
  \titlepage
\end{frame}

@@

@@

\begin{frame}
	\frametitle{Заключение}
	\begin{columns}
		\begin{column}{0.8\textwidth}
			\begin{itemize}
				\item Предложены различные способы моделирования мультимодального распределения в обратном диффузионном процессе

>>>>

	\setbeamertemplate{footline}[page number]
	\setbeamersize{text margin left=1.5em, text margin right=2.0em}
}
\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}
\newcommand\FontUP{\fontsize{10}{12}\selectfont}

@@

{
\begin{frame}
  \titlepage
\end{frame}
}

@@

\begin{frame}
	\frametitle{Литература}
	\FontUP
	\begin{itemize}
		\item Jonathan Ho, Ajay Jain, and Pieter Abbeel. Denoising diffusion probabilistic models, 2020
		\medskip
		\item Zhisheng Xiao, Karsten Kreis, and Arash Vahdat. Tackling the generative learning trilemma with denoising diffusion gans, 2021.
		\medskip
		\item Alex Nichol and Prafulla Dhariwal. Improved denoising diffusion probabilistic models, 2021.
		\medskip
		\item Sebastian Nowozin, Botond Cseke, and Ryota Tomioka. f-gan: Training generative neural samplers using
		variational divergence minimization, 2016.
		\medskip
		\item Martin Arjovsky, Soumith Chintala, and L?on Bottou. Wasserstein gan, 2017.
	\end{itemize}

@@

\begin{frame}
	\frametitle{Заключение}
	\FontUP
	\begin{columns}
		\begin{column}{0.8\textwidth}
			\begin{itemize}
				\item Предложены различные способы моделирования мультимодального распределения в обратном диффузионном процессе
